### 2017-11-10 paper/sections/4_dynamic-policies.tex
paper: start fixing the file system section
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

The actual policy is shown in Figure~\ref{src:lru-dyn} where the only
difference between the code snippet in Figure~\ref{src:lru} is the addition of
lines 2-9. Note that policy also uses the \texttt{RDState} and \texttt{WRState}
functions described in Section~\S\ref{sec:extracting}.

\begin{figure}[t]
\footnotesize
\centering
\begin{minted}[xleftmargin=3em,linenos]{lua}
function when()
  policy = RDState()
  if policy == 0
    if servers[whoami]['cachesize'] > 100K then
      WRState(1)
      policy = 1
    end
  end
  if policy == 1
    if servers[whoami]['cachesize'] > n then
      return true
    end
  end
  return false
end
\end{minted}
\caption{A more complicated LRU-based cache policy that has two parts. After
absorbing the initial burstiness of the workload, the policy switches to a more
constrained cache to limit memory usage. The performance/utilization for
different values of \texttt{n} is shown in
Figure~\ref{fig:methodology-tradeoff-dynamic}. \label{src:lru-dyn}}
\end{figure}

>>>>

The actual policy is shown in Figure~\ref{src:lru-dyn} where the only
difference between the code snippet in Figure~\ref{src:lru} is the addition of
lines 2-7. Note that policy also uses the \texttt{RDState} and \texttt{WRState}
functions described in Section~\S\ref{sec:extracting}.

\begin{figure}[t]
\footnotesize
\centering
\begin{minted}[xleftmargin=3em,linenos]{lua}
function when()
  if server[whoami]['cachesize'] > n then
    if server[whoami]['cachesize'] > 100K then
      WRstate(1)
    end
    if RDstate() == 1 then
      return true
    end
  end
  return false
end
\end{minted}
\caption{A more complicated LRU-based cache policy that has two parts. After
absorbing the initial burstiness of the workload, the policy switches to a more
constrained cache to limit memory usage. The performance/utilization for
different values of \texttt{n} is shown in
Figure~\ref{fig:methodology-tradeoff-dynamic}. \label{src:lru-dyn}}
\end{figure}

### 2017-11-10 paper/sections/5_file-systems.tex
paper: start fixing the file system section
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

The code snippets in Figures~\ref{lua:parsplice} and~\ref{lua:cephfs} are the
policies used in ParSplice and CephFS, respectively.  ParSplice uses policies
to manage its caches and CephFS uses policies to control load balancing, but
they both can be expressed with our data management language.  From a
high-level the ParSplice policy trims the cache if the cache reaches a certain
size {\it and} if it has already absorbed the initial burstiness of the
workload; the CephFS policy migrates load if the metadata load is higher than
the average load {\it and} the current load has been overloaded for more than
two iterations.

\textbf{Condition for ``Overloaded"} (Fig.~\ref{lua:parsplice}:Line 2;
Fig.~\ref{lua:cephfs}:Line 2) - these lines detect whether the node is
overloaded using the ``load" calculated in the load callback; while the load
calculations and thresholds are different, the actual logic is exactly the
same.  Recall that this decision is made locally because there is no global
scheduler or centralized intelligence.

\textbf{State Persisted Across Decisions} (Fig.~\ref{lua:parsplice}:Lines 5,6;
Fig~\ref{lua:cephfs}:Lines 3,4,10) - these lines use Mantle to write/read state
from previous decisions.  For ParSplice, we save a boolean that indicates
whether we have absorbed the workload's initial burstiness. For CephFS, we save
the number of consecutive instances that the server has been overloaded. We
also clear the count (Line 10) if the server is no longer overloaded. The
underlying implementation saves the values to local disk.

\textbf{Condition that Switches Policy} (Fig.~\ref{lua:parsplice}:Line 3;
Fig.~\ref{lua:cephfs}:Line 5) - these lines switch the policies using
information from previous decisions. ParSplice trims its cache once it eclipses
the ``absorb" threshold while CephFS allows balancing when overloaded for more
than two iterations. The persistent state is essential for both of these
policy-switching conditions.

\begin{figure}[t]
\footnotesize
\begin{minted}[xleftmargin=3em,linenos]{lua}
local function when()
  if servers[whoami]["load"] > target then
    if servers[whoami]["load"] > absorb_target then
      WRstate(1)
    end
    if RDstate() == 1 then
      return true
    end
  end
  return false
end
\end{minted}
\caption{ParSplice cache management policy.\label{lua:parsplice}}
\end{figure}

@@

\subsection{Using File System Balancers for ParSplice}
\subsection{Using ParSplice Balancers for File Systems}
\subsection{Visualizing File System Traces like ParSplice Keyspace Traces}

>>>>

In the previous section, we used our data management language and the Mantle
policy engine to design effective cache management strategies for a new service
and domain. In this section, we compare and contrast the policies examined for
file system metadata load balancing in~\cite{sevilla:sc15-mantle} with the ones
designed for cache management in ParSplice. The similarities show how the
``when"/``where"/``how much" abstractions, data anagement language, and policy
engine may be widely applicable to other data management techniques, such as
QoS, scheduling, and batching.

\subsection{File Systems}
From a high-level the ParSplice policy trims the cache if the cache reaches a
certain size {\it and} if it has already absorbed the initial burstiness of the
workload; the CephFS poicy, which is shown in Figure~\ref{srd:lua-cephfs},
migrates load if the metadata load is higher than the average load {\it and}
the current load has been overloaded for more than two iterations.

\textbf{Condition for ``Overloaded"} (Fig.~\ref{src:lru-dyn}: Line 2;
Fig.~\ref{lua:cephfs}: Line 2) - these lines detect whether the node is
overloaded using the ``load" calculated in the load callback; while the load
calculations and thresholds are different, the actual logic is exactly the
same.  Recall that this decision is made locally because there is no global
scheduler or centralized intelligence.

\textbf{State Persisted Across Decisions} (Fig.~\ref{src:lru-dyn}: Lines 4,6;
Fig~\ref{lua:cephfs}: Lines 3,4,10) - these lines use Mantle to write/read state
from previous decisions.  For ParSplice, we save a boolean that indicates
whether we have absorbed the workload's initial burstiness. For CephFS, we save
the number of consecutive instances that the server has been overloaded. We
also clear the count (Line 10) if the server is no longer overloaded. The
underlying implementation saves the values to local disk.

\textbf{Condition that Switches Policy} (Fig.~\ref{src:lru-dyn}: Line 6;
Fig.~\ref{lua:cephfs}: Line 5) - these lines switch the policies using
information from previous decisions. ParSplice trims its cache once it eclipses
the ``absorb" threshold while CephFS allows balancing when overloaded for more
than two iterations. The persistent state is essential for both of these
policy-switching conditions.

@@

\subsection{Using File System Policies for ParSplice}
% mantle policies
\subsection{Using ParSplice Policies for File Systems}
% burstiness of creates then compile

\subsection{Cross-pollinating Policies}
% QoS, MRC, RAD - scheduing
%\subsection{Visualizing File System Traces like ParSplice Keyspace Traces}
